Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-09 acl.2016/acl2016.tex
fucking rewrite

@@

The rest of the paper will be broken up into the following sections. Next, we will describe the phrase-based model and the major implementation components, with particular emphasis on decoding speed. We will then describe modifications to improve decoding speed and present results. We conclude in the last section and discuss future work.

\subsection{Feature Functions}

@@

\section{Proposed Improvements}

@@

\section{Experimental Setup}

@@

\section{Results}

@@

In future, we shall investigate other major components of the decoding algorithm, particularly the language model which has not been touched in this paper. We shall also explore the underlying reasons for the scalability issues in Moses to get a better understanding where potential performance issues can arise. This has application to other algorithms beside MT decoding.

>>>>

The rest of the paper will be broken up into the following sections. The rest of this section will discuss prior work and an outline of the phrase-based model. Section~\ref{sec:Proposed Improvements} will then describe the modifications to improve decoding speed. We describe the experiment setup in Section~\ref{sec:Experimental Setup} and present results Section~\ref{sec:Results}. We conclude in the last section and discuss possible future work.

@@

\subsection{Phrase-Based Model}

@@

\section{Proposed Improvements}
\label{sec:Proposed Improvements}

@@

\section{Experimental Setup}
\label{sec:Experimental Setup}

@@

\section{Results}
\label{sec:Results}

@@

In future, we shall investigate other major components of the decoding algorithm, particularly the language model which has not been touched in this paper. We are also keen to explore the underlying reasons for the scalability issues in Moses to get a better understanding where potential performance issues can arise.
